\documentclass[letterpaper,11pt]{letter} % Standard letter class
\usepackage[utf8]{inputenc} % Handles various character encodings
\usepackage{geometry} % For adjusting margins
\usepackage[hidelinks]{hyperref} % For clickable email/web links without visible boxes
\usepackage{lmodern} % Uses the Latin Modern font, a common alternative to Computer Modern

% Ensure that generated pdf is machine readable/ATS parsable
\input{glyphtounicode}
\pdfgentounicode=1

% --- Sender's Information ---
\name{Kevin Chen}
\address{
    114 Boyd Drive \\
    Rochester, NY 14616 \\
    (585) 797-5153 \\
    \href{mailto:kc681269@gmail.com}{kc681269@gmail.com} \\
    \href{https://www.linkedin.com/in/k3vnc/}{linkedin.com/in/k3vnc/}
}
\signature{Kevin Chen} % This is your typed name that appears after the closing

\begin{document}

% --- Letter Start ---
\begin{letter}{
    Hiring Manager \\ % Standard addressee if no specific name is known
    Fluke Corporation \\
    6920 Seaway Blvd \\
    Everett, WA 98203
}

\opening{Dear Hiring Manager,}

My name is Kevin Chen, and I'm writing to express my interest in the Software Engineering Intern position for Summer 2025 at Fluke as advertised on Indeed.

I have recently completed my third year of Software Engineering at the Rochester Institute of Technology, where I have developed a solid foundation in web development, cloud computing, and core software engineering principles.

The opportunity to contribute to a company like Fluke, particularly in a role that involves developing and enhancing front-end UI components with ReactJS and working with AWS cloud technologies, immediately caught my attention and aligns perfectly with my career aspirations.

Fluke's long-standing reputation for manufacturing rugged, reliable, and accurate industrial tools is particularly compelling. This internship presents an outstanding opportunity for me to apply my skills in a practical environment and learn from industry experts.

This internship would also allow me to deepen my practical experience with AWS services, and to apply my skills in ReactJS and Python, including Flask, to meaningful projects.

My passion lies in creating user friendly applications that effectively meet both user needs and business goals.

Throughout my coursework at RIT, I have gained experience with key technologies listed in the job description. For example, I utilized ReactJS in my enterprise software engineering course to design, develop, integrate, deploy, and maintain a full stack web application. I also have experience with AWS services such as S3, Lambda, and DynamoDB, which I used in my cloud computing course to build a stock sentiment tracker that fetches articles and performs sentiment analysis using AWS Comprehend.

I am also familiar with Agile methodologies, having worked in teams to deliver projects using Agile principles. Furthermore, my coursework emphasized the importance of team collaboration, effective communication, and problem-solving skills, qualities I understand are essential for success in an environment like Fluke.

I am eager to bring my skills in web development, cloud computing, and my proactive learning attitude to Fluke. I am on track to graduate from Rochester Institute of Technology in May 2027, aligning with the qualifications for this internship. My resume, which provides further detail on my projects and technical skills, is attached for your review. Thank you for your time and consideration. I look forward to the possibility of discussing this exciting opportunity with you.

\closing{Sincerely,}

% \encl{Resume} % You can uncomment this if you want to explicitly state "Enclosure: Resume"

\end{letter}
% --- Letter End ---

\end{document}