%-------------------------
% Embedded Resume
% Author : Kevin Chen
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Kevin Chen} \\ \vspace{1pt}
    \small (585) 797-5153 $|$ kc681269@gmail.com $|$ 
    https://www.linkedin.com/in/k3vnc/ 
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rochester Institute of Technology}{Rochester, NY}
      {Bachelor of Science in Software Engineering}{Expected May 2027}
      \resumeItemListStart
        \resumeItem{\textbf{Cumulative GPA: 3.18}}
        \resumeItem{\textbf{Dean's List: Spring 2023, Spring 2025}}
        \resumeItem{\textbf{Relevant Courses:} Eng Cloud Software Systems, Software Testing, Engineering of Enterprise Software Systems, Engineering of Software Subsystems (Embedded), Software Process \& Project Management, Web Engineering, Software Development and Problem Solving 1 \& 2 (Python, Java, Git)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Programming Languages}{: Java, Python, JavaScript, TypeScript, C, C++, C\\#, SQL, Bash.} \\
\textbf{Web Technologies}{: HTML, CSS, React.js, Next.js, Node.js, Express.js, .NET, REST APIs, OAuth 2.0.} \\
\textbf{Databases}{: MongoDB, PostgreSQL, MySQL.} \\
\textbf{Dev Tools}{: Git, VS Code, Linux/Unix, Postman, cURL, Vim, Docker, Jest, Unix/Linux.} \\
\textbf{Other Technologies}{: Apache HTTP Server, STM32Cube, JSON, XML, Selenium.}}}\\
\end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{IoT Environmental Monitor} $|$ \emph{C, STM32 HAL, I2C, UART, AWS IoT}}{2025}
        \resumeItemListStart
          \resumeItem{Created an embedded environmental monitor on an STM32 Nucleo board to collect real-time sensor data, display it locally, and prepare it for cloud transmission.}
          \resumeItem{Configured and utilized microcontroller peripherals including GPIO, UART for serial debugging via a retargeted \texttt{\_write} syscall, and I\textsuperscript{2}C for external device communication.}
          \resumeItem{Integrated a DHT22 temperature/humidity sensor and a 1602 LCD by incorporating third-party drivers and wiring the hardware with appropriate pull-up resistors.}
          \resumeItem{Systematically debugged hardware and software issues, including I\textsuperscript{2}C bus communication failures and peripheral pin-muxing conflicts, using a multimeter and serial log outputs.}
          \resumeItem{Designed the cloud architecture for data ingestion and processing, planning for an ESP32 to publish sensor data via MQTT to \textbf{AWS IoT Core}, triggering a \textbf{Lambda} function to persist time-series data in \textbf{Amazon Timestream}.}
        \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{MIDI Player} $|$ \emph{C, STM32Cube, Git}}{2024}
          \resumeItemListStart
            \resumeItem{Developed a MIDI player using C and a STM32 Nucleo board to parse and play MIDI files.}
            \resumeItem{Generated and played musical notes on a piezo buzzer from parsed MIDI data.}
\resumeItem{Utilized microcontroller peripherals including USART for file transfer, GPIO for button inputs, DAC for audio output, and NVIC for interrupt handling to create a complete embedded audio system.}
            \resumeItem{Implemented features such as track selection, button control through external interrupts, and playback.}
          \resumeItemListEnd
                \resumeProjectHeading
          {\textbf{Enterprise Application Project} $|$ \emph{MERN Stack (MongoDB, Express.js, React,, Node.js, Recharts)}}{2024}
          \resumeItemListStart
            \resumeItem{Designed and implemented a full-stack application using the MERN stack, adhering to departmental and corporate requirements.}
            \resumeItem{Developed and tested a MongoDB-backed RESTful API with Express.js, including endpoints for CRUD operations, database initialization, and unit tests using Jest.}
            \resumeItem{Created a React-based client application, integrating features such as filtering, adding, editing, and deleting data.}
            \resumeItem{Deployed the full application on an Ubuntu server with Node.js and MongoDB, ensuring independent functionality for each department's APIs and client apps.}
            \resumeItem{Collaborated on implementing a consistent corporate theme across all departmental applications with shared landing pages and branding.}
            \resumeItem{Conducted operations reviews with the professor and had frequent team meetings.}
            \resumeItem{Added an integrated dashboard with Recharts for data analytics, providing metrics such as employee breakdowns, sales insights, and cost analysis with interactive visualizations.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{WatchOS Llama App} $|$ \emph{XCode, Groq API}}{2024}
          \resumeItemListStart
            \resumeItem{Created a watchOS app voice to voice chatbot.}
            \resumeItem{Used Groq APIs for Whisper v3 Large and Llama 3.1 70B inference.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd

% %-----------CLUBS-----------
% \section{Student Organizations}
%   \resumeSubHeadingListStart
%     \resumeItem{RIT Democrats}
%     \resumeItem{RIT AI Club}
%   \resumeSubHeadingListEnd

  
%-------------------------------------------
\end{document}