%-------------------------
% Full Stack Resume
% Author : Kevin Chen
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kevin Chen} \\ \vspace{1pt}
    \small (585) 797-5153 $|$ kc681269@gmail.com $|$ Rochester, NY $|$ 
    \href{https://www.linkedin.com/in/k3vnc/}{linkedin.com/in/k3vnc} $|$ 
    \href{https://github.com/kvn8888}{github.com/kvn8888}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rochester Institute of Technology}{Rochester, NY}
      {Bachelor of Science in Software Engineering}{Expected May 2027}
      \resumeItemListStart
        \resumeItem{\textbf{Cumulative GPA: 3.18}}
        \resumeItem{\textbf{Dean's List: Spring 2023, Spring 2025}}
        \resumeItem{\textbf{Relevant Courses:} Eng Cloud Software Systems, Software Testing, Engineering of Enterprise Software Systems, Engineering of Software Subsystems (Embedded), Software Process \& Project Management, Web Engineering, Software Development and Problem Solving 1 \& 2 (Python, Java, Git)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeItem{AWS Certified Cloud Practitioner -- Amazon Web Services, 2025}
    \resumeItem{Ivalua Level 1 (Platform) and Level 2 (Technical and Configuration) Certifications -- Ivalua, 2025}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Programming Languages}{: Java, Python, JavaScript, TypeScript, C, C++, C Sharp, SQL, Bash.} \\
\textbf{Web Technologies}{: HTML, CSS, React.js, Next.js, Node.js, Express.js, Prisma ORM, Flask, .NET, Vercel, REST APIs, OAuth 2.0.} \\
\textbf{Databases}{: MongoDB, PostgreSQL, Microsoft SQL Server, MariaDB.} \\
\textbf{Dev Tools}{: Git, GitHub, GitHub Actions, GitLab (CI/CD, Runner), SVN, Docker, Docker Compose, Nx, VS Code, Visual Studio, Postman, cURL, Vim, Jest, JUnit, Pytest, Unix/Linux.} \\
\textbf{Cloud \& Infra}{: AWS (Lambda, EventBridge, SNS, Comprehend, EC2, S3, CloudWatch, IAM), Terraform, nginx, Vercel.} \\
\textbf{Other Technologies}{: Apache HTTP Server, STM32Cube, JSON, XML, Selenium.}}}\\
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Customer Application Engineer Intern}{Oct 2025 -- Apr 2026}
      {Ivalua}{Fremont, CA (Hybrid)}
      \resumeItemListStart
        \resumeItem{Provide post–go-live support for Ivalua's enterprise procurement platform, validating configuration and data change requests using C\#, .NET, and Microsoft SQL Server.}
        \resumeItem{Diagnosed and resolved a role-based authorization misconfiguration for a major semiconductor client that prevented admin users from assigning required access profiles, restoring correct permissions without disrupting ongoing operations.}
        \resumeItem{Write and execute SQL scripts to clean up customer environments (e.g., removing blank workflows and invalid records) to maintain data integrity and workflow consistency.}
        \resumeItem{Use tools such as Visual Studio, Tortoise SVN, and Microsoft SQL Server Management Studio to debug issues, review changes, and deliver safe, incremental updates.}
        \resumeItem{Participate in weekly team meetings to report progress, discuss blockers, and coordinate next steps with senior engineers, while holding Ivalua Level 1 (Configuration) and Level 2 (Technical) certifications.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{TA Portal -- DevOps \& Infrastructure} $|$ \emph{GitHub Actions, Docker, nginx, Nx, MariaDB} $|$ \emph{RIT SCOOP Program}}{2025}
        \resumeItemListStart
          \resumeItem{Designed a GitHub Actions CI/CD pipeline for an Nx monorepo that ran lint/tests in parallel and deployed only affected services based on branch naming conventions.}
          \resumeItem{Containerized a 4-service architecture (MariaDB, Workflow API, Express.js backend, Next.js frontend) using Docker Compose with health checks, dependency ordering, and persistent volumes for reliable restarts.}
          \resumeItem{Configured an Ubuntu VM with Docker and nginx as a reverse proxy with SSL termination, routing external HTTPS traffic to internal HTTP containers and simplifying application configuration.}
          \resumeItem{Established SSH key-based authentication from GitHub Actions to the production VM and secured access with UFW firewall rules, eliminating manual SSH steps from the deployment process.}
          \resumeItem{Resolved Prisma ORM startup failures and Next.js routing issues behind nginx by updating Dockerfiles and basePath configuration, preventing 404s and container crashes in production.}
          \resumeItem{Authored deployment and troubleshooting documentation covering Docker, nginx, firewall setup, and CI/CD workflows so other team members could maintain and debug the system.}
        \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{Enterprise Application Project} $|$ \emph{MERN Stack, Recharts, Jest} $|$ \emph{Enterprise Engineering Course Project}}{2024}
    \resumeItemListStart
      \resumeItem{Collaborated with a team of four using Agile Methodologies to develop a full-stack MERN application for a simulated enterprise, meeting specified business requirements.}
      \resumeItem{Built and tested a secure RESTful API with Node.js, Express.js, and MongoDB, featuring over 12 CRUD endpoints and achieving 95\% unit test coverage with Jest.}
      \resumeItem{Developed a responsive React client with a Recharts analytics dashboard to visualize key metrics, which improved user task completion time and informed strategic decisions.}
      \resumeItem{Managed the deployment of the full MERN stack to an Ubuntu server, configuring Apache HTTP Server as a reverse proxy to the backend.}
    \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{WatchOS Voice Chatbot} $|$ \emph{SwiftUI, XCode, Groq API, REST} $|$ \emph{Personal Project}}{2024}
        \resumeItemListStart
            \resumeItem{Programmed a proof-of-concept voice-to-voice chatbot on watchOS using SwiftUI for the user interface and AVFoundation for audio capture and playback.}
            \resumeItem{Integrated with the Groq API for near-real-time AI inference, leveraging Whisper for speech-to-text and Llama 3.1 for text generation, achieving an average response time of under 2 seconds.}
            \resumeItem{Engineered the network layer to handle asynchronous API calls and manage data flow between the app and the backend services efficiently.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

% %-----------CLUBS-----------
% \section{Student Organizations}
%   \resumeSubHeadingListStart
%     \resumeItem{RIT Democrats}
%     \resumeItem{RIT AI Club}
%   \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
