%-------------------------
% IoT Resume
% Author : Kevin Chen
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
 
%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kevin Chen} \\ \vspace{1pt}
    \small (585) 797-5153 $|$ kc681269@gmail.com $|$ Rochester, NY $|$ 
    https://www.linkedin.com/in/k3vnc/ 
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rochester Institute of Technology}{Rochester, NY}
      {Bachelor of Science in Software Engineering}{Expected May 2027}
      \resumeItemListStart
        \resumeItem{\textbf{Cumulative GPA: 3.18}}
        \resumeItem{\textbf{Dean's List: Spring 2023, Spring 2025}}
        \resumeItem{\textbf{Relevant Courses:} Eng Cloud Software Systems, Software Testing, Engineering of Enterprise Software Systems, Engineering of Software Subsystems (Embedded), Software Process \& Project Management, Web Engineering, Software Development and Problem Solving 1 \& 2 (Python, Java, Git)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeItem{AWS Certified Cloud Practitioner -- Amazon Web Services, 2025}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}{: JavaScript, TypeScript, Python, Java, C, C++, C\#, SQL, Bash.} \\
\textbf{Frontend}{: HTML, CSS, React.js, Next.js, Tailwind CSS.} \\
\textbf{Backend}{: Node.js, Express.js, .NET, REST APIs, OAuth 2.0, JWT.} \\
\textbf{Databases}{: MongoDB, PostgreSQL.} \\
\textbf{Dev Tools}{: Git, GitHub, GitHub Actions, GitLab (CI/CD, Runner), Docker, Docker Hub, VS Code, Postman, cURL, Vim, Jest, Unix/Linux.} \\
\textbf{Cloud \& Infra}{: AWS (Lambda, EventBridge, SNS, Comprehend, EC2, S3, CloudWatch, IAM), Terraform, Vercel.} \\
\textbf{Other}{: Apache HTTP Server, Selenium, JSON, XML.}}}
\end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Stock Sentiment Tracker} $|$ \emph{AWS, Terraform, Boto3, Python, GitHub Actions, Git} $|$ \emph{Cloud Engineering Course Project}}{2025}
        \resumeItemListStart
          \resumeItem{Architected and co-developed a serverless sentiment analysis platform for stock discussions, reducing manual research time for users with a team of four.}
          \resumeItem{Engineered core AWS Lambda functions with Python (Boto3) to process stock data from DynamoDB and perform sentiment analysis via Amazon Comprehend, achieving a 40\% improvement in data processing speed.}
          \resumeItem{Implemented an automated notification system using EventBridge and SNS, delivering daily email alerts to a user base of 50+ beta testers for their subscribed tickers.}
          \resumeItem{Authored Terraform scripts to provision and manage all cloud infrastructure (EventBridge, Lambda, SNS, IAM), enabling 100\% reproducible environments and cutting down deployment time by 90\%.}
          \resumeItem{Optimized performance by designing logic to bypass sentiment analysis for previously scored entries, reducing redundant API calls to Comprehend by over 60\%.}
        \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{MIDI Player} $|$ \emph{C, STM32Cube, Embedded Systems, Git}}{2024}
          \resumeItemListStart
            \resumeItem{Engineered and programmed a MIDI player on an STM32 Nucleo board, using C to parse MIDI file data structures and generate corresponding audio signals.}
            \resumeItem{Implemented performance optimization by managing hardware resources, including DMA for efficient data transfer and DAC for precise analog waveform generation, producing clear audio on a piezo buzzer.}
            \resumeItem{Designed the system to utilize microcontroller peripherals, including USART for file reception, GPIO for button-based UI, and NVIC for interrupt-driven controls (track selection, play/pause).}
            \resumeItem{Conducted code reviews and debugging sessions to ensure firmware stability and adherence to embedded C best practices.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Enterprise Application Project} $|$ \emph{MERN Stack, Recharts, Jest} $|$ \emph{Enterprise Engineering Course Project}}{2024}
          \resumeItemListStart
            \resumeItem{Collaborated with a team of four to design and develop a full-stack MERN application to meet specified corporate and departmental business requirements for a simulated enterprise.}
            \resumeItem{Built and rigorously tested a secure RESTful API using Node.js and Express.js, featuring over 12 endpoints for full CRUD functionality. Achieved 95\% unit test coverage with Jest.}
            \resumeItem{Developed a responsive React client, enabling users to filter, edit, and visualize data. My contributions led to a 20\% improvement in user task completion time based on usability testing.}
            \resumeItem{Leveraged data structures within MongoDB to organize and query information efficiently, supporting complex data relationships across departments.}
            \resumeItem{Integrated an analytics dashboard with Recharts to provide data-driven insights, visualizing key metrics like sales trends and employee performance which informed strategic decisions in project reviews.}
          \resumeItemListEnd
      \resumeSubHeadingListEnd 

% %-----------CLUBS-----------
% \section{Student Organizations}
%   \resumeSubHeadingListStart
%     \resumeItem{RIT Democrats}
%     \resumeItem{RIT AI Club}
%   \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
